---
output: rmarkdown::github_document
---
```{r include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = TRUE,
                      dev="png", fig.retina = 2, fig.width = 10, fig.height = 6)
```
# misinfo

Tools to Perform 'Misinformation' Analysis on a Text Corpus

## Description

Tools to Perform 'Misinformation' Analysis on a Text Corpus

## What's Inside The Tin

The following functions are implemented:

- `mi_analyze_document`:	Run a one or more documents through a misinformation/bias sentiment analysis
- `mi_plot_document_summary`:	Plot raw frequency count summary from a processed corpus
- `mi_plot_individual_frequency`:	Plot raw frequency count summary from a processed corpus
- `mi_use_builtin`:	Use a built-in 'sentiment' word/phrase list
- `word_doc_to_txt`:	Convert a Word document to a plaintext document

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/misinfo")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(misinfo)
library(tidyverse)

# current verison
packageVersion("misinfo")

```

### Try it out on the built-in corpus

```{r}
mi_analyze_document(
  path = system.file("extdat", package="misinfo"),
  pattern = ".*txt$",
  bias_type = "explanatory",
  sentiment_list = mi_use_builtin("explanatory")
) -> corpus
```

```{r}
glimpse(corpus)
```

```{r}
corpus$frequency_summary
```

```{r}
corpus$individual_frequency
```

```{r fig.height=8}
mi_plot_individual_frequency(corpus)
```

```{r fig.height=8}
mi_plot_individual_frequency(corpus, FALSE)
```

```{r}
mi_plot_document_summary(corpus)
```

```{r}
mi_plot_document_summary(corpus, FALSE)
```



